Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-03 Papers/ms.tex
conditional prior

@@

@@

>>>>

The conditional prior for the data given the parameters
is a product of independent gaussian distributions, one for each pixel.
This is conventionally called the ``sampling distribution'', or sometimes just the ``likelihood''. However, sampling distribution is misleading since no
physical frequency distribution exists which is being sampled from. The term
likelihood is also usually used to refer to the scalar function of the parameters
obtained when the data are known. For a discussion of the view that this
object is really a prior distribution, see \citet[][pp. 33--35]{caticha}.

@@

\newpage
The conditional prior for the data given the parameters
is a product of independent gaussian distributions, one for each pixel.
This is conventionally called the ``sampling distribution'', or sometimes just the ``likelihood''. However, sampling distribution is misleading since no
physical frequency distribution exists which is being sampled from. The term
likelihood is also usually used to refer to the scalar function of the parameters
obtained when the data are known. For a discussion of the view that this
object is really a prior distribution, see \citet[][pp. 33--35]{caticha}.

@@

\bibitem[Caticha(2008)]{caticha} Caticha, A.\ 2008.\ Lectures 
on Probability, Entropy, and Statistical Physics.\ ArXiv e-prints 
arXiv:0808.0012.
